### 2024-07-18 conteudo/methods/methods.tex
Reformulate init of the chapter

To answer our proposed research questions, we opted to divide our research. Firstly, we will approach 
the supplementary research RQ1.1, which will serve as a background to our research question RQ1. 
To answer the RQ1.1, we propose a multiple-method investigation by validating our proposed tool in 
the BigCloneBench dataset \citep{bigclonebench}, which is the standard method used by the literature, 
and an empirical analysis of a selected subset of functions in which the tool infers. With the question 
RQ1.1 answered, we will return our focus to the RQ1. To answer the RQ1, we opted to create an 
ethnographic study using participant-observation methodology. We expect to mitigate a selected subset 
of duplicated functions by refactoring them using a designed systematic approach while interacting 
with the Linux community to collect feedback on the mitigation made by us.

\section{Multiple-method Investigation}

The multiple-method investigation to verify the efficiency of our tool is a method that we 
consider trustworthy. The first method used is to evaluate the proposed tool in the BigCloneBench 
database \citep{bigclonebench} one of the standard code duplication databases used to validate 
the tool presented in the formal literature. As presented by Krinke and Ragkhitwetsagul, the 
BigCloneBench is not a perfect dataset \citep{bigfail}. For that reason, we opted 
to do an additional evaluation, in which we will do an empirical analysis on a select subset of 
functions of the AMD Display driver, which our tool infers is a duplication. For a concrete evaluation,
in both methods, we will apply a variation of the similarity metric (The similarity metric is a 
metric that measures the similarity of two code duplications; a proper explanation is made
in Chapter \ref{cha:tool}).

\subsection{Evaluation by the formal literature}

@@

\subsection{Evaluation by Empirical analyses}

>>>>

To answer our proposed research questions, we opted to do a multiple-method research 
where we covered the research question with different methodologies. To approach the RQ1, 
we opted to create an ethnographic study using participant-observation methodology where 
we plan to mitigate a selected subset of duplicated functions by refactoring them using 
a designed systematic approach while interacting with the Linux community to collect 
feedback on the mitigation made by us.

To answer RQ1, which covers our main objective to mitigate code duplication in the Linux 
kernel, we are first required to be able to identify them. For this reason, we developed 
a tool and need to understand if the tool can identify code duplications in the Linux kernel, 
which covers the supplementary research question RQ1.1 for the RQ1.

To answer RQ1.1, we applied two independent submethods and performed a triangulation of 
the results. The first submethod is to evaluate the proposed tool similarly to the literature, 
by comparing it against the BigCloneBench dataset \citep{bigclonebench}. The second submethod
for answering RQ1.1 is to do an empirical analysis on a selected subset of functions of the 
AMD Display driver that our tool infers is a duplication. With the two submethods completed, 
we will do a triangulation of results analyzing the findings. We opted for the triangulation 
of the two submethods because the formal literature method alone is limited and not fully 
trustworthy \citep{bigfail, litreview}.

\subsection{Evaluation of the tool by the formal literature}

@@

\subsection{Evaluation of the tool by Empirical analyses}
